---
title: "Test gs4_auth"
author: "Ben Best"
date: "5/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}
shelf(
  DT,
  googlesheets4,
  here)

gsheets_sa_json <- switch(
  Sys.info()[["effective_user"]],
  bbest      = "/Volumes/GoogleDrive/My Drive/projects/nms-web/data/nms4gargle-774a9e9ec703.json",
  jai        = "/Volumes/GoogleDrive/My Drive/service-tokens/nms4gargle-774a9e9ec703.json",
  PikesStuff = "/Users/PikesStuff/Theseus/Private/nms4gargle-774a9e9ec703.json")

gsheet <- "https://docs.google.com/spreadsheets/d/1C5YAp77WcnblHoIRwA_rloAagkLn0gDcJCda8E8Efu4/edit"
```

## Setup Service Account API Key

Reference:

- [googlesheets4 auth • googlesheets4](https://googlesheets4.tidyverse.org/articles/articles/auth.html)
- [Non-interactive auth](https://cran.r-project.org/web/packages/gargle/vignettes/non-interactive-auth.html): main reference for understanding this

Steps:

1. Save [nms4gargle-774a9e9ec703](https://drive.google.com/file/d/1LTvMM74gYB5MAkspiTqjA4BiTzVLTgNp/view?usp=sharing) locally, in this case to `r gsheets_sa_json`.

  1. Manage [shares – IAM & Admin – nms4gargle – Google Cloud Platform](https://console.cloud.google.com/iam-admin/serviceaccounts/details/111162214432618062602?authuser=2&project=nms4gargle). Added permissions to : jai.ranganathan@gmail.com, pike.spector@noaa.gov.
  
1. Share [Master_OCNMS_infographic_content - Google Sheets](`r gsheet`) to `shares@nms4gargle.iam.gserviceaccount.com`.


## Use

```{r}
stopifnot(file.exists(gsheets_sa_json))

gs4_auth(path = gsheets_sa_json)

sheet_names(gsheet)

tbl_modals <- read_sheet(gsheet, "figures")

datatable(tbl_modals)
```


