---
pagetitle: "Algae and surfgrass"
---

```{r setup, include=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F, error=F)
source(here::here("infographiqR.R"))
```

`r insert_info(csv = here::here("data/gsheets/modals.csv"))`

## {.tabset}

### Map of Sites

```{r}
rocky_map("ocnms")
```

`r insert_caption('rocky-shore_macroalgae-surfgrass.html', 'Map of Sites')`

### Interactive Trends - Rockweed {.active}

```{r}
rocky_tsplot(rocky_cover, "OCNMS", "PELLIM", "Rockweed", "pelvetiopsis") # %>%
  # dyLegend(show="follow")
```

`r insert_caption('rocky-shore_macroalgae-surfgrass.html', 'Interactive Trends - Rockweed')`

### Interactive Trends - Surfgrass

```{r}
rocky_tsplot(rocky_cover, "OCNMS", "PHYSPP", "Surfgrass", "phyllospadix") # %>%
  # dyLegend(show="follow")
```

`r insert_caption('rocky-shore_macroalgae-surfgrass.html', 'Interactive Trends - Surfgrass')`

### Trends - Rockweed

`r insert_figure("rocky-shore_macroalgae-surfgrass.html", "figures/S.H.10._Pelvetiopsis_SokolPt_MARINe.jpg")`

### Trends - Surfgrass

`r insert_figure("rocky-shore_macroalgae-surfgrass.html", "figures/S.H.10.4_Surfgrass_MARINe.jpg")`
