---
pagetitle: "Ochre stars"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F, error=F)
source(here::here("infographiqR.R"))
```

`r insert_info(csv = here::here("data/gsheets/modals.csv"))`

## {.tabset}

### Map of Sites

```{r}
rocky_map("ocnms")
```

`r insert_caption('rocky-shore_mussels.html', 'Map of Sites')`

### Interactive Trends - Ochre stars {.active}

```{r}
rocky_tsplot(
  rocky_counts, "OCNMS", "PISOCH", "Ochre Seastar") # %>% 
  # dyLegend(show="follow")
```

`r insert_caption('rocky-shore_ochre-star.html', 'Interactive Trends - Ochre stars')`

### Trends - Size at Pt. Grenville

`r insert_figure("rocky-shore_ochre-star.html", "figures/Appendix S.LR.12.1 - Size structure of Pisaster ochraceus in rocky shore habitats Pt Grenville.jpg")`

### Trends - Size at Sokol Point

`r insert_figure("rocky-shore_ochre-star.html", "figures/Appendix S.LR.12.1 - Size structure of Pisaster ochraceus in rocky shore habitats Sokol Pt.jpg")`

<!-- OLD: missing in [Master_OCNMS_infographic_content - Google Sheets](https://docs.google.com/spreadsheets/d/1C5YAp77WcnblHoIRwA_rloAagkLn0gDcJCda8E8Efu4/edit#gid=1464497539)
#### Trends - status & condition

r insert_figure("rocky-shore_ochre-star.html", "figures/S.H.12.*_seastar_S&T_ONP.jpg")

#### Trends - sunflower star

r insert_figure("rocky-shore_ochre-star.html", "figures/Appendix S.LR.12.3a - Counts of Pycnopodeia helianthoides in rocky shores 2006-2015.jpg")
-->
